Conflict-Free Vertex Coloring of Planar Graphs

### 2017-04-15 presentation/presentation.tex
Pretty close to done with presentation

    \only<1-2>{
      \begin{itemize}
        \item<1-2> \textbf{Simple graph}: undirected graph with no loops.
        \pause
        \vfill
        \item \textbf{Planar graph}: no edges overlap.
      \end{itemize}
    }

    \only<3-5>{
      \begin{itemize}
        \item<3-5> \textbf{Neighborhood} of a vertex $v$: a set of all vertices adjacent to $v$ plus $v$.
        \vfill
        \only<3>{\item<4> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
        \only<4>{\item<4> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
        \only<5>{\item<5> Example: The neighborhood of vertex 5: $\{1, 2, 4, 5, 6\}$.}
      \end{itemize}
    }

@@

    \only<11-13>{
    \vspace{0.55cm}
      \begin{itemize}
        \item \textbf{Dominating set}: a subset of vertices $D$ of $V$ such that every vertex \emph{not} in $D$ is adjacent to at least one vertex in $D$.
        \vfill
        \only<11>{\item<7> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
        \only<12>{\item<12> Example: $\{2, 5\}$}
        \only<13>{\item<13> Example: $\{2, 4\}$}
      \end{itemize}
    }

@@

    \begin{itemize}
      \item A \textbf{proper vertex coloring} of a graph $G$ assigns colors to \emph{every} vertex such that no two adjacent vertices share the same color.
      \pause
      \vfill
      \item The \textbf{chromatic number} of $G$ is the minimum number of colors needed to properly color $G$.
    \end{itemize}
  \end{frame}

@@

    \begin{itemize}
      \item<1-2> A \textbf{conflict-free coloring} of a graph $G$ assigns colors to \emph{some} vertices such that the neighborhood of every vertex contains at least one unique color.
      \vfill
      \pause
      \item<2> Proper vertex colorings are also conflict-free colorings.
    \end{itemize}
  \end{frame}

@@

    \begin{center}
      Every vertex $v$ has at least one unique color within its neighborhood.
    \end{center}

@@

    \begin{columns}
      \begin{column}{0.5\textwidth}
        \begin{itemize}[leftmargin=1.4cm]
          \item[$v$ = 1:] $\{1: none,\ 2: none,\ 5: \textbf{red}\}$
          \item[$v$ = 2:] $\{1: none,\ 2: none,\ 3: \textbf{blue},$ \newline $\quad 5: red,\ 6: none\}$
          \item[$v$ = 3:] $\{2: none,\ 3: \textbf{blue}\}$
        \end{itemize}
      \end{column}

@@

      \begin{column}{0.5\textwidth}
        \begin{itemize}[leftmargin=1.4cm]
          \item[$v$ = 1:] $\{1: \textbf{blue},\ 2: red,\ 5: yellow\}$
          \item[$v$ = 2:] $\{1: blue,\ 2: \textbf{red},\ 3: blue,$ \newline $\quad 5: yellow,\ 6: blue\}$
          \item[$v$ = 3:] $\{2: red,\ 3: \textbf{blue}\}$
        \end{itemize}
      \end{column}
    \end{columns}

@@

    \only<1-2>{
      \begin{figure}[h]
        \centering
        \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/bad-criterion-1.pdf}
        \caption*{Graphs $K_3$ and $K_4$, respectively}
      \end{figure}
    }

    \only<3>{
      \begin{figure}[h]
        \centering
        \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/bad-criterion-2.pdf}
        \caption*{Graphs $K_3$ and $K_4$, respectively}
      \end{figure}
    }

    \only<4>{
      \begin{figure}[h]
        \centering
        \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/bad-criterion.pdf}
        \caption*{Graphs $K_3$ and $K_4$, respectively}
      \end{figure}
    }

@@

    \begin{textblock*}{14cm}(1cm, 1.6cm) % {block width} (coords)
      Let's demonstrate meeting this criterion on a graph for the simplest case, $k=1$:
    \end{textblock*}

    \begin{textblock*}{15cm}(0.5cm, 2.1cm) % {block width} (coords)
      \only<1>{
        \begin{figure}
         \centering
         \includegraphics[width=6cm]{../figures/criterion.pdf}
         \caption*{A simple, undirected graph $G$}
       \end{figure}
      }

      \only<2>{
        \vspace{0.25cm}
        \begin{columns}
          \begin{column}{0.5\textwidth}
            \begin{center}
              \begin{figure}
                 \centering
                 \includegraphics[width=6cm]{../figures/criterion.pdf}
                 \caption*{A simple, undirected graph $G$}
               \end{figure}
            \end{center}
          \end{column}
          \begin{column}{0.5\textwidth}
            \begin{center}
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/bad-criterion.pdf}
                \caption*{Graphs $K_{3}$ and $K_{4}^{-3}$}
              \end{figure}
            \end{center}
          \end{column}
        \end{columns}
      }

      \only<3>{
        \vspace{0.25cm}
        \begin{columns}
          \begin{column}{0.5\textwidth}
            \begin{center}
              \begin{figure}
                 \centering
                 \includegraphics[width=6cm]{../figures/criterion-minor.pdf}
                 \caption*{A simple, undirected graph $G$}
               \end{figure}
            \end{center}
          \end{column}
          \begin{column}{0.5\textwidth}
            \begin{center}
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/bad-criterion.pdf}
                \caption*{Graphs $K_{3}$ and $K_{4}^{-3}$}
              \end{figure}
            \end{center}
          \end{column}
        \end{columns}
      }
    \end{textblock*}

    \begin{textblock*}{14cm}(1cm, 7.1cm) % {block width} (coords)
      A graph is a \textbf{minor} if it can be formed by deleting and/or contracting edges from its parent graph. To be conflict-free colored with 1 color, graph $G$ cannot contain $K_3$ or $K_4^{-3}$ as a minor.  \only<3>{$G$ contains both $K_3$ and $K_4^{-3}$ as a minor and thus {\color{red}\textbf{cannot}} be conflict-free colored with 1 color.}
    \end{textblock*}

>>>>

    \only<1-2>{
      \begin{itemize}
        \item \textbf{Simple graph}: undirected graph with no loops.
        \pause
        \vfill
        \item \textbf{Planar graph}: no edges cross.
      \end{itemize}
    }

    \only<3-5>{
      \begin{itemize}
        \item<3-5> \textbf{Neighborhood} of a vertex: a set of all adjacent vertices and the vertex itself.
        \vfill
        \only<3>{\item<4> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
        \only<4>{\item<4> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
        \only<5>{\item<5> Example: The neighborhood of vertex 5: $\{1, 2, 4, 5, 6\}$.}
      \end{itemize}
    }

@@

    \only<11-13>{
    \vspace{0.55cm}
      \begin{itemize}
        \item \textbf{Dominating set}: all vertices outside of the set must have distance 1 to some vertex within the set.
        \vfill
        \only<11>{\item<7> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
        \only<12>{\item<12> Example: $\{2, 5\}$}
        \only<13>{\item<13> Example: $\{2, 4\}$}
      \end{itemize}
    }

@@

    \begin{itemize}
      \item A \textbf{proper vertex coloring} assigns colors to \emph{every} vertex such that no two adjacent vertices share the same color.
      \pause
      \vfill
      \item The \textbf{chromatic number} is the minimum number of colors needed to properly color a graph.
    \end{itemize}
  \end{frame}

@@

    \begin{itemize}
      \item<1-2> A \textbf{conflict-free coloring} assigns colors to \emph{some} vertices such that the neighborhood of every vertex contains at least one uniquely colored vertex.
      \vfill
      \pause
      \item<2> Proper vertex colorings are also conflict-free colorings.
    \end{itemize}
  \end{frame}

@@

@@

    \begin{columns}
      \begin{column}{0.5\textwidth}
        \begin{multicols}{2}
          \begin{itemize}[leftmargin=1.4cm]
            \item[1:] \textbf{red}
            \pause
            \item[2:] \textbf{blue}
            \pause
            \item[3:] \textbf{blue}
            \pause
            \item[4:] \textbf{red}
            \pause
            \item[5:] \textbf{red}
            \pause
            \item[6:] \textbf{red}
          \end{itemize}
        \end{multicols}
      \end{column}

@@

      \begin{column}{0.5\textwidth}
        \begin{multicols}{2}
          \begin{itemize}[leftmargin=1.4cm]
            \item[1:] \textbf{blue}
            \pause
            \item[2:] \textbf{red}
            \pause
            \item[3:] \textbf{blue}
            \pause
            \item[4:] \textbf{red}
            \pause
            \item[5:] \textbf{yellow}
            \pause
            \item[6:] \textbf{blue}
          \end{itemize}
        \end{multicols}
      \end{column}
    \end{columns}

@@

    \only<1-2>{
      \begin{figure}[h]
        \centering
        \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/bad-criterion-1.pdf}
        \caption*{Complete 3 vertex and complete 4 vertex graphs}
      \end{figure}
    }

    \only<3>{
      \begin{figure}[h]
        \centering
        \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/bad-criterion-2.pdf}
        \caption*{Complete 3 vertex and complete 4 vertex graphs}
      \end{figure}
    }

    \only<4>{
      \begin{figure}[h]
        \centering
        \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/bad-criterion.pdf}
        \caption*{Complete 3 vertex and tattered 4 vertex graphs}
      \end{figure}
    }

@@

    \begin{textblock*}{14cm}(1cm, 1.6cm) % {block width} (coords)
      Let's demonstrate meeting this criterion on a graph for the simplest case, 1 color.
    \end{textblock*}

    \begin{textblock*}{15cm}(0.5cm, 2.1cm) % {block width} (coords)
      \only<1>{
        \begin{figure}
         \centering
         \includegraphics[width=6cm]{../figures/criterion.pdf}
         \caption*{A simple graph}
       \end{figure}
      }

      \only<2>{
        \vspace{0.25cm}
        \begin{columns}
          \begin{column}{0.5\textwidth}
            \begin{center}
              \begin{figure}
                 \centering
                 \includegraphics[width=6cm]{../figures/criterion.pdf}
                 \caption*{A simple graph}
               \end{figure}
            \end{center}
          \end{column}
          \begin{column}{0.5\textwidth}
            \begin{center}
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/bad-criterion.pdf}
                \caption*{Complete 3 vertex and tattered 4 vertex graphs}
              \end{figure}
            \end{center}
          \end{column}
        \end{columns}
      }

      \only<3>{
        \vspace{0.25cm}
        \begin{columns}
          \begin{column}{0.5\textwidth}
            \begin{center}
              \begin{figure}
                 \centering
                 \includegraphics[width=6cm]{../figures/criterion-minor.pdf}
                 \caption*{A simple graph}
               \end{figure}
            \end{center}
          \end{column}
          \begin{column}{0.5\textwidth}
            \begin{center}
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/bad-criterion.pdf}
                \caption*{Complete 3 vertex and tattered 4 vertex graphs}
              \end{figure}
            \end{center}
          \end{column}
        \end{columns}
      }

      \only<4>{
        \begin{textblock*}{14cm}(1cm, 3.5cm) % {block width} (coords)
          \begin{theorem}
          A graph cannot be conflict-free colored with $k$ colors if it contains a complete graph of $k+2$ vertices or a tattered graph of $k+3$ vertices.
          \end{theorem}
        \end{textblock*}
      }
    \end{textblock*}

    \begin{textblock*}{14cm}(1cm, 7.1cm) % {block width} (coords)
      A graph is a \textbf{minor} if it can be formed by deleting and/or contracting edges from its parent graph.  \only<3->{$G$ contains both graphs as a minor and thus {\color{red}\textbf{cannot}} be conflict-free colored with 1 color.}
    \end{textblock*}
